\documentclass[11pt,a4paper]{moderncv}
\moderncvstyle{classic} 
\moderncvcolor{blue}
\setlength{\hintscolumnwidth}{2.5cm} 
\usepackage[utf8]{inputenc}
\usepackage[top=1.1cm, bottom=1.1cm, left=2cm, right=2cm]{geometry}
\usepackage{multicol}

\firstname{Pierre}
\familyname{Vigier}
\title{Master student}
\email{pierre.vigier@epfl.ch}
\homepage{pvigier.github.io}
\social[linkedin]{pierrevigier}
\social[github]{pvigier}
\begin{document}
\makecvtitle

\section{Education}
\cventry{2017 -- present}{MSc in Computer Science}{EPFL}{Lausanne}{}{Information Theory and Coding, Cryptography and Security, Machine Learning, Foundations of Software, Intelligent Agents, Advanced Computer Graphics and Advanced Algorithms.}
\cventry{2015 -- present}{MOOCs}{Stanford, EPFL, UCSD}{}{}{Machine Learning, Functional Programming, Computer Graphics, Automata, Data Mining and Game Theory.}
\cventry{2015 -- 2017}{Engineering School}{CentraleSupélec}{Gif-sur-Yvette}{}{Probability, Statistics, Signal Processing, Software Engineering, Algorithms, Networks, Operating Systems, Computer Architecture, Numerical Methods, Big Data and Electrical Engineering.}
\cventry{2013 -- 2015}{Preparatory classes for grandes écoles}{Lycée Louis-le-Grand}{Paris}{}{Foundations in Mathematics, Physics and Computer Science.}
\cventry{2012 -- 2013}{Baccalauréat Série S}{Lycée Madame de Staël}{Montluçon}{}{With the highest honors.}

\section{Experience}
\cventry{June 2017 -- August 2017}{Research intern}{LIMOS}{Clermont-Ferrand}{}{Detection of arthritis using medical images of hands.}

\section{Skills}

%\begin{multicols}{2}
%\setlength{\maincolumnwidth}{\linewidth-\leftskip-\rightskip-\separatorcolumnwidth-\hintscolumnwidth}

\cvitem{Programming}{\begin{itemize}
\item C, C++ (OpenGL)
\item Java, Scala (Spark)
\item Python (Scientific libraries, PyTorch, TensorFlow)
\item Matlab, \LaTeX (Beamer)
\item HTML5, CSS3, JavaScript (jQuery), Django, SQL
\end{itemize}}

\cvitem{Systems}{Linux (Debian), Windows}

%\columnbreak

\cvitem{Languages}{\begin{itemize}
\item French (mother tongue)
\item English (advanced)
\item Spanish (beginner)
\end{itemize}}

%\end{multicols}

\section{Side projects}
\cvitem{2017 -- present}{Member of PolyGameDev (EPFL).}
\cvitem{}{Project manager and developer for the video game Vagabond.}
\cvitem{2015}{Won the Challenge Startup Kick-off (Université Paris-Saclay).}
\cvitem{2013}{$2^{nd}$ prize at the \textit{Olympiades académiques de chimie} (Clermont-Ferrand).}
\cvitem{2012}{$1^{st}$ prize at the \textit{Olympiades académiques de mathématiques} (Clermont-Ferrand).}
\cvitem{Hobbies}{Reading (sci-fi and fantasy), 3D modeling, video game programming.}

\end{document}